---
title: "Group Project"
author: "Brandon Güell, Dani Antos, Isabella, Muratore"
date: "11/7/2017"
output: html_document
toc: true
toc_float: true
number_sections: true
Preliminaries:
---

To start out these are the packages we need:
````{r}
install.packages("adegenet", dep=TRUE)
install.packages("phangorn", dep=TRUE)
```
Then lets load the packages using:
```{r}
library(stats)
library(ade4)
library(ape)
library(adegenet)
library(phangorn)
```

#Objectives
In this module, we will develop phylogenetic tree making skills......

#Introduction
Phylogenetic treesa re useful......

The three types of tree making methods we will discuss are:

MAKE TABS for each three of the three methods!!!!

1) XXXX----- explanation

2) XXX---- explanation

3) XX--- explanation


#Useful skills we will go over today:
-list of stuff
-list 
-list
-list

#Read in the dataset from XXXXXX using this chunk:
```{r}
dna <- fasta2DNAbin(file="http://adegenet.r-forge.r-project.org/files/usflu.fasta")
```

then lets read in another thing....
```{r}
annot <- read.csv("http://adegenet.r-forge.r-project.org/files/usflu.annot.csv", header=TRUE, row.names=1)
```



#Additional Resources and Useful Links
-links
-links
-links

#Citations
-citations of stuff we used